\documentclass[a4paper]{exam}

\usepackage{amsmath,amssymb, amsthm}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titling}



% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS/MATH 113, SPRING 2025}{WC 01: \LaTeX practice and introduction to logic}{\theauthor}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

% \printanswers %Uncomment this line

\title{Weekly Challenge 01: \LaTeX\; practice and introduction to logic}
\author{mm10357} % <=== replace with your student ID, e.g. xy012345
\date{CS/MATH 113 Discrete Mathematics\\Habib University\\Spring 2025}

\qformat{{\large\bf \thequestion. \thequestiontitle}\hfill}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}
  
\titledquestion{Everythings on the table} Draw the truth table of the implication operator.
\begin{solution}
\hspace{3cm}\textit{Implication Truth Table}
\centering\begin{tabular}{|c|c|c|}
  \hline
  P & Q & $P \implies Q$ \\
  \hline
  T & T & T \\
  T & F & F \\
  F & T & T \\
  F & F & T \\
  \hline
  \end{tabular}
\end{solution}

\titledquestion{Triangles!} Write the Pythagorean theorem.
\begin{solution}
   The Pythagorean Theorem states that in a right triangle, the square of the length of the hypotenuse is equal to the sum of the squares of the lengths of the other two sides. Mathematically,
\[
a^2 + b^2 = c^2,
\]
where $a$ and $b$ are the lengths of the two sides, and $c$ is the length of the hypotenuse.
Definition Source: Chatgpt
\end{solution}

\titledquestion{That feeling when knee surgery is tomorrow} Consider the statement ``If Luigi was a mansplaining cat then shrek will give you knee surgery tomorrow''. Given then Luigi is an italian human plumber what can you say about the above statement?

Elaborate your answers in 2 to 3 sentences by referencing to the relevant row(s) in the truth table.
\begin{solution}
The statement provided is: "If Luigi was a mansplaining cat, then Shrek will give you knee surgery tomorrow." Let $P$ represent "Luigi is a mansplaining cat" and $Q$ represent "Shrek gives you knee surgery tomorrow." The statement can be expressed as $P \implies Q$
Given that Luigi is an Italian human plumber, $P$ is false. The truth table of $P \implies Q$ states that when $P$ is false, the implication $P \implies Q$ is true regardless of the truth value of $Q$. Thus, the statement in this case will be true.
\end{solution}


      
\end{questions}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
